ggalluvial: Layered Grammar for Alluvial Plots

### 2023-01-30 README.rmd
tweak titular vignette + reformat package names + suppress warnings in tests

This is a [**ggplot2** extension](https://exts.ggplot2.tidyverse.org/) for alluvial plots.

@@

The alluvial plots implemented here can be used to visualize frequency distributions over time or frequency tables involving several categorical variables. The design is inspired by the [**alluvial**](https://github.com/mbojan/alluvial) package, but the **ggplot2** framework induced several conspicuous differences:

- **alluvial** understands a variety of inputs (vectors, lists, data frames), whereas **ggalluvial** requires a single data frame;
- **alluvial** uses each variable of these inputs as a dimension of the data, whereas **ggalluvial** requires the user to specify the dimensions, either as separate aesthetics or as [key-value pairs](https://tidyr.tidyverse.org/);
- **alluvial** produces both the _alluvia_, which link cohorts across multiple dimensions, and (what are here called) the _strata_, which partition the data along each dimension, in a single function; whereas **ggalluvial** relies on separate layers (stats and geoms) to produce strata, alluvia, and alluvial segments called _lodes_ and _flows_.

Additionally, **ggalluvial** arranges these layers vertically without gaps, so that the secondary plotting axis indicates the cumulative values of the strata at each dimension.

@@

The development version can be installed from the (default) `main` branch on GitHub:
```{r eval=FALSE}
remotes::install_github("corybrunson/ggalluvial@main", build_vignettes = TRUE)
```
Note that, in order to build the vignettes, the imported packages **alluvial**, **ggfittext**, and **ggrepel** must be installed. To skip this step, leave `build_vignettes` unspecified or set it to `FALSE`.

@@

The data is in "wide" format, but **ggalluvial** also recognizes data in "long" format and can convert between the two:

@@

For detailed discussion of the data formats recognized by **ggalluvial** and several examples that illustrate its flexibility and limitations, read the technical vignette:

@@

For some more digestible guidance on using **ggalluvial**, check out three cheat sheets and demos by students in Joyce Robbins's [Exploratory Data Analysis and Visualization Community Contribution Project](https://jtr13.github.io/cc21fall2/index.html):

@@

If you use **ggalluvial**-generated figures in publication, i'd be grateful to hear about it! You can also cite the package according to `citation("ggalluvial")`.

>>>>

This is a [{ggplot2} extension](https://exts.ggplot2.tidyverse.org/) for alluvial plots.

@@

The alluvial plots implemented here can be used to visualize frequency distributions over time or frequency tables involving several categorical variables. The design is inspired by the [{alluvial}](https://github.com/mbojan/alluvial) package, but the {ggplot2} framework induced several conspicuous differences:

- {alluvial} understands a variety of inputs (vectors, lists, data frames), whereas {ggalluvial} requires a single data frame;
- {alluvial} uses each variable of these inputs as a dimension of the data, whereas {ggalluvial} requires the user to specify the dimensions, either as separate aesthetics or as [key-value pairs](https://tidyr.tidyverse.org/);
- {alluvial} produces both the _alluvia_, which link cohorts across multiple dimensions, and (what are here called) the _strata_, which partition the data along each dimension, in a single function; whereas {ggalluvial} relies on separate layers (stats and geoms) to produce strata, alluvia, and alluvial segments called _lodes_ and _flows_.

Additionally, {ggalluvial} arranges these layers vertically without gaps, so that the secondary plotting axis indicates the cumulative values of the strata at each dimension.

@@

The development version can be installed from the (default) `main` branch on GitHub:
```{r eval=FALSE}
remotes::install_github("corybrunson/ggalluvial@main", build_vignettes = TRUE)
```
Note that, in order to build the vignettes, the imported packages {alluvial}, {ggfittext}, and {ggrepel} must be installed. To skip this step, leave `build_vignettes` unspecified or set it to `FALSE`.

@@

The data is in "wide" format, but {ggalluvial} also recognizes data in "long" format and can convert between the two:

@@

For detailed discussion of the data formats recognized by {ggalluvial} and several examples that illustrate its flexibility and limitations, read the technical vignette:

@@

For some more digestible guidance on using {ggalluvial}, check out three cheat sheets and demos by students in Joyce Robbins's [Exploratory Data Analysis and Visualization Community Contribution Project](https://jtr13.github.io/cc21fall2/index.html):

@@

If you use {ggalluvial}-generated figures in publication, i'd be grateful to hear about it! You can also cite the package according to `citation("ggalluvial")`.
